---
title: "StackOverFlow Survey 2023"
output: 
  flexdashboard::flex_dashboard:
    theme: yeti
    social: menu
    orientation: columns    
    vertical_layout: fill
engine: shiny
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(stringr)
library(highcharter)
library(tidyverse)

# Read the dataset
survey <- read.csv('survey.csv')

# Assuming your dataset is named 'survey'
edlevel_data <- reactive({
  survey %>% 
    filter(!is.na(EdLevel)) %>%  
    group_by(EdLevel) %>%
    summarise(count = n()) %>%
    mutate(percentage = (count / sum(count)) * 100) %>%
    arrange(desc(percentage))
})

learning_data <- reactive({
  survey %>% 
    filter(!is.na(LearnCode) & !grepl("Other \\(please specify\\)", LearnCode)) %>%  
    separate_rows(LearnCode, sep = ";") %>%
    group_by(LearnCode) %>%
    summarise(count = n()) %>%
    mutate(percentage = (count / nrow(survey)) * 100) %>%
    arrange(desc(percentage))
})

learning_online <- reactive({
  survey |> 
    filter(!is.na(LearnCodeOnline) & !grepl("Other \\(Please specify\\)", LearnCodeOnline)) |>
    separate_rows(LearnCodeOnline, sep = ";") |>
    group_by(LearnCodeOnline) |>
    summarise(count = n()) |>
    mutate(percentage = (count / nrow(survey)) * 100) |>
    arrange(desc(percentage)) |>
    top_n(10)
    
})


online_courses <- reactive({
  survey|>
  filter(!is.na(LearnCodeCoursesCert)) |>
  separate_rows(LearnCodeCoursesCert, sep = ";") |>
  group_by(LearnCodeCoursesCert) |>
  summarise(count = n())  |>
  mutate(percentage = (count/ nrow(survey |>filter(!is.na(LearnCodeCoursesCert)))) * 100) |>
  arrange(desc(percentage))
})



generate_highchart <- function(data, chart_type, display_option, xAxisCategories) {
  if (display_option == "By Percentage") {
    chart <- highchart() %>%
      hc_chart(type = chart_type) %>%
      hc_xAxis(categories = xAxisCategories) %>%
      hc_yAxis(title = list(text = "Percentage")) %>%
      hc_tooltip(pointFormat = "Percentage: {point.y:.2f}%") %>%
      hc_plotOptions(
        series = list(dataLabels = list(enabled = TRUE, format = "{point.y:.2f}%"))
      ) %>%
      hc_add_series(data = data$percentage, name = "Percentage") %>%
      hc_legend(enabled = FALSE)
  } else {
    chart <- highchart() %>%
      hc_chart(type = chart_type) %>%
      hc_xAxis(categories = xAxisCategories) %>%
      hc_yAxis(title = list(text = "Count")) %>%
      hc_tooltip(pointFormat = "Count: {point.y}") %>%
      hc_plotOptions(
        series = list(dataLabels = list(enabled = TRUE, format = "{point.y}"))
      ) %>%
      hc_add_series(data = data$count, name = "Count") %>%
      hc_legend(enabled = FALSE)
  }

  return(chart)
}


output$edlevel_chart <- renderHighchart({
  data <- edlevel_data()
  chart_type <- "bar"
  display_option <- input$display_option
  xAxisCategories <- data$EdLevel  # Adjust this line based on the structure of your data
  generate_highchart(data, chart_type, display_option, xAxisCategories)
})


output$learning_chart <- renderHighchart({
  data <- learning_data()
  chart_type <- "bar"
  display_option <- input$display_option
  xAxisCategories <- data$LearnCode  # Adjust this line based on the structure of your data
  generate_highchart(data, chart_type, display_option, xAxisCategories)
})

output$learning_online_chart <- renderHighchart({
  data <- learning_online()
  chart_type <- "bar"
  display_option <- input$display_option
  xAxisCategories <- data$LearnCodeOnline  # Adjust this line based on the structure of your data
  generate_highchart(data, chart_type, display_option, xAxisCategories)
})


output$online_courses_chart <- renderHighchart({
  data <- online_courses()
  chart_type <- "bar"
  display_option <-input$display_option
  xAxisCategories <- data$LearnCodeCoursesCert
  
  generate_highchart(data, chart_type, display_option, xAxisCategories)
})



prog_online <- function(data, column, separator, count_column, display_option, top_n = NULL) {
  data %>%
    filter(!is.na({{column}}) & !grepl("Other \\(Please specify\\)", {{column}})) %>%
    separate_rows({{column}}, sep = {{separator}}) %>%
    group_by({{column}}) %>%
    summarise(count = n()) %>%
    mutate(percentage = (count / nrow(data)) * 100) %>%
    arrange(desc(percentage)) %>%
    top_n(ifelse(is.null(top_n), n(), top_n))
}




```

Developer Insights {data-icon="fa-users"} 
=====================================  

Inputs {.sidebar}
-------------------------------------

```{r}
radioButtons("display_option", "Display Option:",
             choices = c("By Percentage", "By Count"),
             selected = "By Percentage")
```

Row
-------------------------------------
    
### Education Level
    
```{r}
# Create the Highchart:
highchartOutput("edlevel_chart")
```
 
### How are people learning to code?
    

```{r}
highchartOutput("learning_chart")

``` 

Row
-------------------------------------
    
### Top 10 resources for learning to code.
    
```{r}
highchartOutput("learning_online_chart")
```
    
### Top Online Learning Platforms

```{r}
highchartOutput("online_courses_chart")
```


TechTrends {data-icon="fa-line-chart"} 
=====================================  

Inputs {.sidebar}
-------------------------------------


```{r}
selectInput("dropdown", "Select Category", choices = c("Programming, scripting, and markup languages", "Databases","Cloud platforms", "Web frameworks and technologies", "Other frameworks and libraries", "Other tools","Integrated development environment", "Asynchronous tools", "Synchronous tools"))
```

Column 
-------------------------------------
    
### Chart 1
    
```{r}
highchartOutput('prog_lang_chart')
```
   
Column {.tabset}
-------------------------------------
   
### Chart 2

```{r}
```   
 
### Chart 3
    
```{r}
```



About {data-icon="fa-question"} 
=====================================  
This application was developed by [Soham Bhagwat](sohambhagwat.tech) to find the trends in the homeschooling in the United States.

The data is collected by [Washington Post](https://www.washingtonpost.com/) and is available [here](https://github.com/washingtonpost/data_home_schooling/).

The application is built with the [Shiny](http://shiny.rstudio.com) framework for the [R programming language](https://www.r-project.org/). The application layout is produced with the [flexdashboard](http://rstudio.github.io/flexdashboard/index.html) package, and the charts and maps use [Plotly](http://plot.ly), [Highcharts](http://www.highcharts.com/), and [ggplot2](http://ggplot2.org/), all accessed through their corresponding R packages.


To learn more about my work, [visit my website](https://sohambhagwat.tech) or [connect with me on Linkedin](https://www.linkedin.com/in/soham-bhagwat/).

I'm actively looking for entry level Data Scientist and Data Engineer roles and my resume can be found [here](https://www.sohambhagwat.tech/pdf/Soham_Bhagwat.pdf) or the best way to reach me is via [email](sohambhagwat2@gmail.com) 


